%-------------------------



% Resume in Latex

% Author: Shakra Shamim

%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}

\usepackage[empty]{fullpage}

\usepackage{titlesec}

\usepackage{marvosym}

\usepackage[usenames,dvipsnames]{color}

\usepackage{verbatim}

\usepackage{enumitem}

\usepackage[hidelinks]{hyperref}

\usepackage{fancyhdr}

\usepackage[english]{babel}

\usepackage{tabularx}

\usepackage{fontawesome5}

\usepackage{multicol}

\setlength{\multicolsep}{-3.0pt}

\setlength{\columnsep}{-1pt}

\input{glyphtounicode}

\pagestyle{fancy}

\fancyhf{}

\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}

\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}

\addtolength{\evensidemargin}{-0.5in}

\addtolength{\textwidth}{1.19in}

\addtolength{\topmargin}{-.7in}

\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom

\raggedright

\setlength{\tabcolsep}{0in}

\titleformat{\section}{

  \vspace{-6pt}\scshape\raggedright\large\bfseries

}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{

  \vspace{-2pt}\item

    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}

      \textbf{#1} & \textbf{\small #2} \\

      \textit{\small#3} & \textit{\small #4} \\

    \end{tabular*}\vspace{-6pt}

}

\newcommand{\resumeProjectHeading}[2]{

    \item

    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}

      \small#1 & \textbf{\small #2}\\

    \end{tabular*}\vspace{-6pt}

}

\newcommand{\resumeItemListStart}{\begin{itemize}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------

\begin{center}

    {\Huge \scshape Akash Singh} \\ \vspace{4pt}

   

    \small \faPhone\ +91-9516860979 ~ 

    \href{mailto:akash19ei004@satiengg.in}{\faEnvelope\ \underline{akash19ei004@satiengg.in}} ~ 

    \href{https://www.linkedin.com/in/akash-singh-kushwah-027788382/}{\faLinkedin\ \underline{linkedin}} ~ 

    \href{https://github.com/Akash17Kushwah?tab=repositories}{\faGithub\ \underline{github}} 

\end{center}

%-----------EDUCATION-----------

\section{Education}

\resumeSubHeadingListStart

  \resumeSubheading

  {Samrat Ashok technological Institute, Vidisha}{2019-2023}

    {B.Tech,Electronics and Instrumentation Engineering}

    {CGPA: 7.6/10}

    

\resumeSubHeadingListEnd

%-----------SKILLS-----------

\section{Skills}

\textbf{Languages }  Java, SQL, HTML, CSS, JavaScript. \\

\textbf{Technology \& Tools} Spring Boot, Spring Security, Spring Data JPA, React, ReactJS, NodeJS, Thymeleaf, JSP, JUnit, Maven, Git, GitHub, MySQL, MongoDB, AWS, IntelliJ IDEA, Postman, Tailwind CSS, Bootstrap. \\

%-----------WORK EXPERIENCE-----------

\section{Work Experience}

\resumeSubHeadingListStart


  \resumeSubheading

    {Teacher}{January 2019 -- Present}

    {Udemy}{Online}

    \resumeItemListStart

      \resumeItem{Designed and delivered high-quality online courses on Udemy, focusing on Java, Spring Boot, and full-stack development.}

      \resumeItem{Helped thousands of students globally enhance their coding skills through practical projects and clear, beginner-friendly instruction.}

    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{PROJECTS}

    \vspace{-5pt}

    \resumeSubHeadingListStart

     \resumeProjectHeading

          {\href{https://www.udemy.com/course/build-production-ready-rest-api-with-spring-boot-expense-manager-api/}{\textbf{\large{\underline{Build REST APIs with Spring and Spring Boot}}} \href{https://www.udemy.com/course/build-production-ready-rest-api-with-spring-boot-expense-manager-api/}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Spring Boot, Spring Security, Data JPA, MySQL, MongoDB, AWS, Postman}}}{Udemy Course}\\

          \resumeItemListStart

            \resumeItem {\normalsize{Created a production-grade REST API course that connects to MySQL database through JPA/Hibernate.}}

            \resumeItem{\normalsize{Comprehensive course covering Spring Boot, Spring Security, Data JPA, and database integration with practical examples.}}

            \resumeItem{\normalsize{Project repository: \href{https://github.com/scbushan05/expense-manager-api}{github.com/scbushan05/expense-manager-api}}}

          \resumeItemListEnd 

          \vspace{-13pt}

     \resumeProjectHeading

          {\href{https://youtu.be/jnY9PWhmQSc}{\textbf{\large{\underline{AI Background Remover}}} \href{https://youtu.be/jnY9PWhmQSc}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Spring Boot, React, Tailwind CSS, MySQL, Clerk, Full Stack}}}{2024}\\

          \resumeItemListStart

            \resumeItem {\normalsize{Built a powerful AI-powered Background Remover SaaS Application using React, Spring Boot, and Razorpay integration.}}

            \resumeItem{\normalsize{Full-stack application with modern UI/UX, payment gateway integration, and AI-powered image processing capabilities.}}

          \resumeItemListEnd 

          \vspace{-13pt}

    \resumeProjectHeading

          {\href{https://youtu.be/7eZtiuhgIgc}{\textbf{\large{\underline{Online Food Delivery Application}}} \href{https://youtu.be/7eZtiuhgIgc}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Spring Boot, React, Bootstrap, MongoDB, AWS, IntelliJ IDEA, Full Stack}}}{2024}\\

          \resumeItemListStart

            \resumeItem {\normalsize{Built full-stack online food delivery application for a small restaurant business with admin panel that manages food and orders.}}

            \resumeItem{\normalsize{Implemented complete order management system, menu management, and real-time order tracking functionality.}}

          \resumeItemListEnd 

          \vspace{-13pt}

    \resumeProjectHeading

          {\href{https://youtu.be/_UNE39gZrV4}{\textbf{\large{\underline{Freelance Retail Billing Software}}} \href{https://youtu.be/_UNE39gZrV4}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Spring Boot, React, Bootstrap, MySQL, AWS, IntelliJ IDEA, Full Stack}}}{2024}\\

          \resumeItemListStart

            \resumeItem {\normalsize{Developed a freelance retail product for an electronics business that automates their billing system.}}

            \resumeItem{\normalsize{Complete billing solution with inventory management, invoice generation, and sales reporting features.}}

          \resumeItemListEnd 

          \vspace{-13pt}

    \resumeProjectHeading

          {\href{https://youtu.be/ewGbjpFmRbw}{\textbf{\large{\underline{Authify by Spring Security}}} \href{https://youtu.be/ewGbjpFmRbw}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Spring Boot, Spring Security, React, Bootstrap, MySQL, IntelliJ IDEA}}}{2024}\\

          \resumeItemListStart

            \resumeItem {\normalsize{Implemented secure REST APIs using Spring Security and JWT token authentication that connects to MySQL database.}}

            \resumeItem{\normalsize{Comprehensive authentication and authorization system with JWT-based token management and role-based access control.}}

          \resumeItemListEnd 

          \vspace{-13pt}

    \resumeProjectHeading

          {\href{https://youtu.be/_H5mqb40Yro}{\textbf{\large{\underline{Spring Boot - Todo List}}} \href{https://youtu.be/_H5mqb40Yro}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Spring Boot, Thymeleaf, Bootstrap, MySQL, IntelliJ IDEA}}}{2024}\\

          \resumeItemListStart

            \resumeItem {\normalsize{Created a simple yet powerful todo application with beautiful UI design using Spring Boot and Thymeleaf.}}

            \resumeItem{\normalsize{Full CRUD operations with database persistence, user-friendly interface, and responsive design.}}

          \resumeItemListEnd 

          \vspace{-13pt}

    \resumeSubHeadingListEnd

\section{Coding Profiles} 

Github: \href{https://github.com/Akash17Kushwah?tab=repositories}{\textbf{Akash17Kushwah}} \\

Codeforces: \href{https://codeforces.com/profile/Kushwah17AkashSingh}{\textbf{kushwah17AkashSingh}}\\

leetCode: \href{https://leetcode.com/u/Kushwah17Akash/}{\textbf{Kushwah17Akash}}\\

%-----------ACHIEVEMENTS-----------

\section{Achievements}

\resumeItemListStart

  \resumeItem{22k+ Subscribers on YouTube - Built a thriving tech-focused YouTube channel with 22k+ subscribers by consistently creating high-quality tutorials, project walkthroughs, and career guidance content.}

  \resumeItem{Premium Courses on Udemy - Created and published high-quality premium courses on Udemy, empowering thousands of students worldwide to learn Java, Spring Boot, and full-stack development.}

  \resumeItem{GitHub Contributions - Actively contributed to open-source projects on GitHub, shared reusable code libraries, and consistently maintained personal repositories featuring full-stack applications.}

\resumeItemListEnd

%-----------CERTIFICATIONS-----------

\section{Certifications}

  Coding Blocks - \href{https://drive.google.com/file/d/1rukz6f8zhsKbS0cEqV3p3VOxTg8oG9v2/view?pli=1}{\textbf{Java Core \& Advanced}}\\

HackerRank -

\href{https://www.hackerrank.com/certificates/4fe4301646fa}{\textbf{Problem Solving}}\\

Google -

\href{https://drive.google.com/file/d/1kbj-UpOfyV0sSt5jFUGLb7ZmI8Au3npu/view}{\textbf{Codejam}}\\

Google -

\href{https://drive.google.com/file/d/1onldp9anTuMIPQMjDP2XggDgRrUhR0aI/view?usp=sharing}{\textbf{KickStart}}\\

 

\end{document}

